% Header data
\Name{Haidong Xu}
\Role{Full Stack Platform Engineer (React + Python)}
\Contacts{
  \ContactItem{\faPhone}{+49 176 2337 9496}{}\ContactSep
  \ContactItem{\faEnvelope}{esoteriker.dev@gmail.com}{mailto:esoteriker.dev@gmail.com}\ContactSep
  \ContactItem{\faLinkedin}{LinkedIn}{https://www.linkedin.com/in/haidong-xu/}\ContactSep
  \ContactItem{\faGithub}{GitHub}{https://github.com/Esoteriker}\ContactSep
  \ContactItem{\faGlobe}{About Me}{https://openblog-chi.vercel.app/}
}

% Section labels
\newcommand{\SectionSummary}{Professional Summary}
\newcommand{\SectionWorkExperience}{Work Experience}
\newcommand{\SectionProjects}{Projects}
\newcommand{\SectionEducation}{Education and Certifications}
\newcommand{\SectionSkills}{Core Skills}

% Summary bullets
\newcommand{\SummaryTitle}{Profile}
\newcommand{\SummaryBullets}{
  \item Platform-oriented full stack engineer delivering mission-critical desktop and web systems in industrial environments.
  \item Built Angular plus WebView2 desktop applications with C\# host integration, JS-to-C\# bridge messaging, and packaging workflows [DETAIL?].
  \item Integrated Java and Python services, gRPC-Web communication, and Cypress CI workflow automation to improve cross-module reliability and release confidence.
  \item Improved frontend runtime performance by 18\% through data visualization rendering and data-flow optimization in production dashboards.
}

% Experience entries
\newcommand{\ExpOneCompany}{Siemens Digital Industries Software}
\newcommand{\ExpOneLocation}{G\"ottingen, Germany}
\newcommand{\ExpOneTitle}{Software engineer (full-time)}
\newcommand{\ExpOneTime}{08.2022 -- Present}
\newcommand{\ExpOneBullets}{
  \item Owned desktop platform module boundaries and integration contracts, reducing release churn and improving delivery predictability across frontend, backend, and mobile teams.
  \item Architected Angular plus WebView2 desktop runtime with C\# UI host, enabling secure native host integration for Windows application workflows.
  \item Implemented JS-to-C\# bridge message contracts, enabling reliable bidirectional communication between web UI and desktop host services.
  \item Designed Cypress CI workflow automation for multi-module user journeys, strengthening cross-boundary validation and release confidence for desktop and web updates.
  \item Led Java and Python APIs integration into client workflows, stabilizing cross-service data exchange and reducing interface regressions across delivery cycles.
  \item Built scheduler application using gRPC-Web, coordinating backend-client communication for reliable task dispatch and status synchronization.
}

\newcommand{\ExpTwoCompany}{}
\newcommand{\ExpTwoLocation}{}
\newcommand{\ExpTwoTitle}{Software engineer (part-time)}
\newcommand{\ExpTwoTime}{10.2021 -- 08.2022}
\newcommand{\ExpTwoBullets}{
  \item Built typed internal component framework, improving reuse, interface consistency, and maintainability across shared frontend modules.
  \item Optimized data visualization rendering and data flow, achieving 18\% runtime performance improvement on complex production dashboards.
}

% Project entries
\newcommand{\ProjectOneName}{\href{https://www.wfp.org/hunger-map}{WFP Hunger-Map}}
\newcommand{\ProjectOneBullets}{
  \item Designed Next.js and TypeScript architecture with UI, data, and domain boundaries, improving maintainability for long-term feature delivery.
  \item Integrated AI-powered external services through API abstraction with timeout, retry, and fallback handling, improving continuity during upstream instability.
}

\newcommand{\ProjectTwoName}{Master thesis}
\newcommand{\ProjectTwoBullets}{
  \item Built secure backend interfaces connecting web frontend with EDA services, enabling unified submission and status visibility for long-running workloads.
  \item Implemented async job execution and status tracking with Docker-based deployment, improving operational reproducibility and multi-service handover.
}

% Education entries
\newcommand{\EduOneSchool}{Technische Universit\"at M\"unchen}
\newcommand{\EduOneDegree}{M.Sc Information System}
\newcommand{\EduOneLocation}{M\"unchen, Germany}
\newcommand{\EduOneTime}{10.2022-12.2025}

\newcommand{\EduTwoSchool}{Georg-August-Universit\"at G\"ottingen}
\newcommand{\EduTwoDegree}{B.Sc Business Informatics}
\newcommand{\EduTwoLocation}{G\"ottingen, Germany}
\newcommand{\EduTwoTime}{10.2019-08.2022}

\newcommand{\EduCertSchool}{Google Data Analytics Professional Certificate}
\newcommand{\EduCertDegree}{}
\newcommand{\EduCertLocation}{}
\newcommand{\EduCertTime}{06.Dec.2021}

% Skills
\newcommand{\SkillFrontendLabel}{Frontend}
\newcommand{\SkillDesktopLabel}{Desktop}
\newcommand{\SkillAutomationLabel}{Automation}
\newcommand{\SkillBackendLabel}{Backend}
\newcommand{\SkillAILabel}{AI Integration}
\newcommand{\SkillArchitectureLabel}{Architecture}

\newcommand{\SkillFrontend}{React, TypeScript, Angular, Next.js}
\newcommand{\SkillDesktop}{Desktop application development, Angular plus WebView2 plus C\# host, JS-to-C\# bridge, native host integration}
\newcommand{\SkillAutomation}{Cypress CI workflow automation, end-to-end automation, cross-boundary validation}
\newcommand{\SkillBackend}{Java services, Python API integration, gRPC-Web, microservices collaboration, Docker deployment}
\newcommand{\SkillAI}{LLM API integration, API abstraction, timeout and retry and fallback resilience}
\newcommand{\SkillArchitecture}{API design, async workflows, status tracking, security-aware design, English collaboration}
