% Header data
\Name{Haidong Xu}
\Role{Software Engineer}
\Contacts{
  \ContactItem{\faPhone}{+49 176 2337 9496}{}\ContactSep
  \ContactItem{\faEnvelope}{esoteriker.dev@gmail.com}{mailto:esoteriker.dev@gmail.com}\ContactSep
  \ContactItem{\faLinkedin}{LinkedIn}{https://www.linkedin.com}\ContactSep
  \ContactItem{\faGithub}{GitHub}{https://github.com}\ContactSep
  \ContactItem{\faGlobe}{About Me}{https://esoteriker.dev}
}

% Section labels
\newcommand{\SectionWorkExperience}{Work Experience}
\newcommand{\SectionProjects}{Academic Projects}
\newcommand{\SectionEducation}{Education and Certifications}
\newcommand{\SectionSkills}{Technical and Language Skills}

% Experience entries
\newcommand{\ExpOneCompany}{Siemens Digital Industries Software}
\newcommand{\ExpOneLocation}{G\"ottingen, Germany}
\newcommand{\ExpOneTitle}{Software engineer (full-time)}
\newcommand{\ExpOneTime}{08.2022 -- Present}
\newcommand{\ExpOneBullets}{
  \item Delivered production features for a large-scale industrial web platform, focusing on data processing workflows, system integration, and performance-critical modules instead of UI-only implementation.
  \item Built end-to-end Cypress regression pipelines across frontend-backend boundaries, improving release confidence, reducing risk during rollout, and strengthening long-term reliability.
  \item Compiled native C++ libraries to WebAssembly (WASM) to reuse high-performance business logic in the web runtime without duplicating complex implementations in JavaScript.
  \item Contributed to architecture decisions on module boundaries, data flow, and build pipelines, helping improve platform scalability, maintainability, and team development efficiency.
  \item Owned the full lifecycle (build, test, and release) of the Testlab mobile application while collaborating across web, backend, and mobile engineering layers.
  \item Developed and maintained Java backend services and stable APIs to ensure reliable client-server integration and predictable behavior across product modules.
}

\newcommand{\ExpTwoCompany}{}
\newcommand{\ExpTwoLocation}{}
\newcommand{\ExpTwoTitle}{Software engineer (part-time)}
\newcommand{\ExpTwoTime}{10.2021 -- 08.2022}
\newcommand{\ExpTwoBullets}{
  \item Designed and maintained a typed, reusable internal component framework, improving cross-team consistency, enforceable contracts, and long-term maintainability.
  \item Optimized data visualization pipelines for complex datasets and achieved an 18\% runtime performance improvement through rendering and data-flow improvements.
  \item Refactored legacy modules during incremental modernization, improving code structure, testability, and alignment with modern engineering standards and practices.
}

% Project entries
\newcommand{\ProjectOneName}{\href{https://www.wfp.org/hunger-map}{WFP Hunger-Map}}
\newcommand{\ProjectOneBullets}{
  \item Designed and developed a scalable, production-ready web system with Next.js and TypeScript, with clear separation of presentation, data access, and business logic layers.
  \item Contributed to system architecture with emphasis on performance, reliability, and maintainability under real-world usage and deployment constraints.
  \item Integrated AI-powered external services, including API design, failure handling, and resilience strategy for unstable upstream dependencies.
}

\newcommand{\ProjectTwoName}{Master thesis}
\newcommand{\ProjectTwoBullets}{
  \item Developed a secure backend system connecting a web frontend with multiple EDA tool services in a unified interface.
  \item Designed a modular backend architecture covering user, project, job, and logging modules for clear ownership and extensibility.
  \item Implemented asynchronous job execution and status tracking to support long-running EDA workloads and reliable progress visibility.
  \item Deployed the system in a Docker-based runtime environment for reproducible setup and easier operational handover.
}

% Education entries
\newcommand{\EduOneSchool}{Technische Universit\"at M\"unchen}
\newcommand{\EduOneDegree}{M.Sc Information System}
\newcommand{\EduOneLocation}{M\"unchen, Germany}
\newcommand{\EduOneTime}{10.2022-12.2025}

\newcommand{\EduTwoSchool}{Georg-August-Universit\"at G\"ottingen}
\newcommand{\EduTwoDegree}{B.Sc Business Informatics}
\newcommand{\EduTwoLocation}{G\"ottingen, Germany}
\newcommand{\EduTwoTime}{10.2019-08.2022}

\newcommand{\EduCertSchool}{Google Data Analytics Professional Certificate}
\newcommand{\EduCertDegree}{}
\newcommand{\EduCertLocation}{}
\newcommand{\EduCertTime}{06.Dec.2021}

% Skills
\newcommand{\SkillProgrammingLabel}{Programming}
\newcommand{\SkillFrameworksLabel}{Frameworks/Libraries}
\newcommand{\SkillToolsLabel}{Tools}
\newcommand{\SkillPMLabel}{Project management}
\newcommand{\SkillLanguagesLabel}{Languages}

\newcommand{\SkillProgramming}{Java, TypeScript, Python, C\#}
\newcommand{\SkillFrameworks}{Angular, React.js, Next.js, Express, Node.js, Spring Boot, FastAPI}
\newcommand{\SkillTools}{Git, GitLab, Jira, Docker, Cypress}
\newcommand{\SkillPM}{Agile development, Scrum}
\newcommand{\SkillLanguages}{English (Professional), German (Professional), Chinese (Native)}
